Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-31 manuscript_wesbrook-bigmacc_BS2021.tex
Updates from Overleaf

Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{ncdc} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990). This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems. Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems [X attribution science report for 2020]. Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above [X cobenefits of adaptation paper]. Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming. This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other landuses. Mitigation and adaptation strategies though are rarely evaluated simultaneously in the context of urban development.

@@

The resulting simulation database can be used to assess decarbonization pathways that align with development trajectories and/or different degrees of global warming. The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space. Several (\citep{various MACC papers}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point countered by \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework. Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.

@@

\subsection*{Mitigation and adaptation decision tools}
\citet{Rysanek MACC} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization. The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were inauthentic. Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness. \citet{kesicki} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs. Traditionally MACCs were developed for annual-planning and more recently, as ambition has grown, so too have their temporal scales. These interactions can be summarized as understanding how investments made in the past may affect the outcome of the MACC, similar to the issue of technical and economic interactions. In planning buildings or infrastructure with MACCs this becomes a significant feature to consider as selecting investments to implement, one typically does so along an investment pathway.

@@

\subsection*{Boundary conditions}
The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{CCworldweathergen}. These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{SSPs} to adjust the hourly values contained in an EPW file. Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.

The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{CMIP6 text}. The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure. Morphed variables and ensemble composition is described in Table \ref{tab:model_table} The morphing process produced four morphed EPWs from two climate change pathways at two time periods, described in Figure \ref{fig:weatherfiles}.

@@

\subsection*{Simulation}
For each development period and under each climate change pathway the same eight strategies for decarbonization and adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development Strategies were tested on their own and in an exhaustive combination with the other seven strategies. The simulation procedure for each scenario began with the base-case, under which no strategies were implemented, following with 255 iterations where strategies where implemented alone and in combination with each other. This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model. The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{multithreading package}. At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes. In each scenario only 16 experiments required unique radiation profiles. These were run first in the loop of 256. The 240 simulations that followed then copied the appropriate output files from the radiation analysis. District heating primary energy requirement was modeled post-simulation as the system present in Wesbrook Village is nuanced to its efficiency and fuel source over the day. This process is described in the following section on "Operational and embodied carbon".

@@

\subsection*{Total Annualized Cost}
Cost of components and technologies was gathered through several data sources, \citep{data sources for cost}. The authors recognize that cost is a highly uncertain data point to incorporate into building models. While the entire capital and operating cost of each building is not encompassed the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible. Cost is assessed as total annualized cost in \ref{eq:TAC}, where X is X, X is X, and X is X.

@@

The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{embodied carbon sources}, and are cradle-to-gate accounts of embodied carbon. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before reaching out for data from further away.

>>>>

Atmospheric concentrations of carbon dioxide lie northward of 410 parts per million, while recent estimates from the \citet{ncdc} situate the Northern Hemisphere’s land and ocean surface temperature anomaly at 1.29°C from baseline (1961-1990). This may not be considered a consistent level of \textit{global warming}, but it does point the dangerous warming trend facing human and non-human systems. Due to the cumulative warming of the planet, climate change impacts are now being recognized as burdens on economic and social systems \citep{Frame et al.}. Implementing adaptation strategies within the built environment is necessary to increase social resilience, protect safety and life, and prevent economic damage with the potential to bolster all of the above \citep{ Schünemann}. Simultaneously, the mitigation of present emissions, the abatement of possible future emissions, and the sequestration of atmospheric carbon is necessary to curtail increasingly dangerous and catastrophic levels of warming. This process of carbon drawdown is very familiar within studies of the built environment with strategies posed for transportation, buildings, agriculture, forestry, and other landuses. Mitigation and adaptation strategies though are rarely evaluated simultaneously in the context of urban development.

@@

The resulting simulation database can be used to assess decarbonization pathways that align with development trajectories and/or different degrees of global warming. The difficulty though is in interpreting a large quantity of simulation data for its salience in the decarbonization and adaptation space. Several (\citep{afsahri; ibhrahim}) have proposed marginal abatement cost curves (MACCs) as a useful metric to compare strategies, while \citet{kesicki} points out that their use should be tempered with caution related to the lack of interaction of strategies in typical MACCs, a point taken up in \citet{rysanek MACC} through an underlying sequential and exhaustive simulation framework. Applying this same framework to the task of determining optimal decarbonization pathways through mitigation strategies can result in a viable set of MACCs for planing and policy support.

@@

\subsection*{Mitigation and adaptation decision tools}
\citet{Rysanek MACC} expanded on the use of marginal abatement cost curves as a tool for planning retrofit pathways in single building optimization. The authors commentary was that by failing to consider technical and economic interactions MACCs such as those proposed by \citet{Mckinnsey} were more \textit{illustrative} than planning tools. Without accounting for the additionality of measures many MACCs fall into this grouping and limit their overall effectiveness. \citet{kesicki} acknowledges temporal interactions as an additional dimension that need to be considered when constructing MACCs. Traditionally MACCs were developed for annual-planning and more recently, as ambition has grown, so too have their temporal scales. These interactions can be summarized as understanding how investments made in the past may affect the outcome of the MACC, similar to the issue of technical and economic interactions. In planning buildings or infrastructure with MACCs this becomes a significant feature to consider as selecting investments to implement, one typically does so along an investment pathway.

@@

\subsection*{Boundary conditions}
The EnergyPlus Weather (EPW) file for Vancouver, BC produced by \citet{CWEC 2016 citation} was morphed, following the algorithms set out by \citet{Belcher} and expanded upon by \citet{jentsch}. These methods utilize the monthly delta of a region's between historical climate models and a projected pathway \citep{oneil kreiglar} to adjust the hourly values contained in an EPW file. Variations on the morphing process have been found, accounting for different shortcomings or the availability of more resolute climate model data to describe a region's specific topographic or climatic uniqueness that may not be captured in a typical climate model's often 100km x 100km grid.

The morphing process in this study differs from previous examples in that it was able to make use of the latest generation of global climate models \citep{oneil tebaldi}. The morphing process took into account an ensemble of 24 models for calculating projected hourly temperature, solar radiation, cloud cover, relative humidity, wind speed, and air pressure. Morphed variables and ensemble composition is described in Table \ref{tab:model_table} The morphing process produced four morphed EPWs from two climate change pathways at two time periods, described in Figure \ref{fig:weatherfiles}.

@@

\subsection*{Simulation}
For each development period and under each climate change pathway the same eight strategies for decarbonization and adaptation to a changing climate were evaluated for their marginal cost of carbon abatement across the whole the Wesbrook development Strategies were tested on their own and in an exhaustive combination with the other seven strategies. The simulation procedure for each scenario began with the base-case, under which no strategies were implemented, following with 255 iterations where strategies where implemented alone and in combination with each other. This was repeated across both development pathways and both climate change pathways, leading to 1024 iterations of the model. The advantage of the underlying simulation technology, CEA, is that demand forecasting can be performed parallelized through multithreading, greatly improving processing time at three minutes per iteration \citep{mckerns}. At the time of writing radiation analysis was not able to be brought out of a single CPU core and thus steps were taken to minimize the amount of times the command was used as the processing time for the ~120 buildings in the UBEM was 25 minutes. In each scenario only 16 experiments required unique radiation profiles. These were run first in the loop of 256. The 240 simulations that followed then copied the appropriate output files from the radiation analysis. District heating primary energy requirement was modeled post-simulation as the system present in Wesbrook Village is nuanced to its efficiency and fuel source over the day. This process is described in the following section on "Operational and embodied carbon".

@@

\subsection*{Total Annualized Cost}
Cost of components and technologies was gathered through several data sources, \citep{rs means; corix cpcn; ctbuh 3for2; kegal; salasobich}. The authors recognize that cost is a highly uncertain data point to incorporate into building models. While the entire capital and operating cost of each building is not encompassed the cost of components and technologies that are affected by strategies are included, making the calculation of net cost between the base-case and an intervention plausible. Cost is assessed as total annualized cost in \ref{eq:TAC}, where X is X, X is X, and X is X.

@@

The embodied carbon of components and technologies of the models was gathered, similarly to the cost data, from a variety of sources \citep{ec3, ICE db, Rodriguez Droguett, Rodriguez}, and are cradle-to-gate accounts of embodied carbon. The limitation with disparate data sources in this portion of the research generally has to do with the geography of the components involved. An effort was made to first gather data from sources specific the BC or the Pacific Northwest region of the US and than from North America as a whole, before reaching out for data from further away.
